Predicting the Quality of CDRH3 Antibody Loop Structural Models

### 2022-10-05 paper.tex
First set of changes and queries

\newcommand{\e}[1]{\mbox{$\times 10^{#1}$}}
\newcommand{\etal}{~\emph{et al.}}
\newcommand{\degree}{\mbox{${}^{\circ}$}}
\newcommand{\lilian}[1]{{\color{red}\sout{#1}}}
\newcommand{\andrew}[1]{{\color{green}\uline{#1}}}

@@

\begin{abstract}
  Therapeutic antibodies have shown an unprecedented pace of
  development and have brought new hope for the treatment of numerous
  diseases. The bioinformatic tools for modelling antibody structures
  have become invaluable for antibody engineering and the development
  of therapeutic antibodies. The antigen-binding site consists of six
  hypervariable loops, also known as the Complementary Determining
  Regions (CDR), all of which can be modelled with adequate accuracy,
  except for one. It remains markedly difficult to model the third CDR
  loop of the antibody heavy chain. The CDR-H3 differs in length, has
  far greater sequence variability and has such a great structural
  diversity that modelling it is considerably harder.

  Many sophisticated approaches for antibody modelling, such as the
  abYmod software, have been developed. Although such efforts have
  improved prediction accuracy the results for the CDR-H3 loop are
  still inconsistent and require further improvement. Providing a
  confidence score for the structure predictions would aid in
  differentiating well-modelled structures from incorrectly modelled
  structures, giving the abYmod user a clearer understanding of the
  generated model reliability.

@@

Antibodies are highly specialized proteins of the immune system that
are produced in response to a foreign substance, called an antigen. A
mature antibody binds a specific antigen with high affinity, while
only weakly interacting with other antigens, or not at all. This high
affinity, high specificity sets it apart from other pharmaceuticals.
Furthermore, in contrast with small drug molecules, antibodies can not
only bind pockets, but also flat, concave or even convex
surfaces\cite{Tavers2001}. Their unique characteristics have enabled 
researchers to develop efficient antibody drugs for treating cancers,
autoimmune disorders, infectious diseases and many more\cite{Lu2020}.
Their ability to target an immense variety of antigens allows for
endless possibilities in application. The global market size was
valued at USD 130.9 billion in 2020, estimated to grow 223.7 billion
by the end of 2025 at a compound annual growth rate of
11.31\%\cite{market2020}. Four of the top 10 best-selling drugs in
2020 were monoclonal antibodies\cite{Urquhart2021}.

In order to rationally design therapeutic antibodies, knowledge of
their structure is essential. The acquired structural information can
be used to increase binding affinity to a target of interest,
predicting both the exact binding site and the antibody stability as
well as assessing immunogenicity\cite{Abhinandan2007}. As
experimental structure determination is very costly and time
consuming, computational predictions of an antibody's structure are
used to streamline the process.

Antibodies consist of a heavy and a light chain, which are linked by
disulphide bonds. The N-terminal domain of each makes up the variable
fragment (Fv), which contains the complementarity determining regions
(CDRs). The antigen binding site is composed of six CDRs, also known
as hypervariable loops. All except one of these loops can be clustered
into a limited number of canonical structures. Therefore, modelling
these loops with adequate accuracy is commonly
achievable\cite{North2011,Weitzner2015}. However, the CDR loop 3 of
the 
heavy chain (CDR-H3) has a far greater sequence variability due to the
processes of V(D)J recombination and somatic hyper‐mutation and its
structure has remained unclassifiable\cite{Finn2016}. The variety in
structure is so great, that its structural diversity is remarkable
even compared to other protein loops\cite{Regep2017}. It was found
that over 75\% of CDR-H3 loops do not have a sub-{\AA}ngstr\"{o}m non-antibody
structural neighbour, as well as that 30\% of CDR-H3 loops have a
completely unique structure compared with under 3\% for all other
loops on average\cite{Regep2017}.

Apart from being the most structurally diverse, the CDR-H3 loop is
also the most important for antigen binding, being located at the
center of the binding site and forming the most contacts to the
antigen\cite{MacCallum1996}. In fact, it was demonstrated that
differences in this loop alone were sufficient to enable otherwise
identical antibodies to distinguish between various
antigens\cite{Xu2000}.

According to the Kabat definition, the CDR-H3 loop is made up of the
residues 95--105 (Kabat numbering scheme\cite{Kabat1992}) in the heavy
chain, with a potential insertion site at position 100. The
possibility of such an insertion of a varying number of residues leads
to a large range of loop lengths, with bovine antibodies being
exceptionally long (Figure~\ref{fig:loopdist}).

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{loopdist.eps}
  \caption { Distribution of CDR-H3 loop lengths in mouse (left),
    human (centre) and cow (right). Mouse and human antibody CDR-H3s
    have a unimodal, yet almost normal distribution with a range of
    $\sim$4--28 and 4--38 respectively. The length cut-off for CDR-H3s
    depicted above is 30 amino acids. Bovine antibodies with
    significantly longer CDR-H3 loops than depicted here exist,
    reaching a length of 67 amino acids and
    above\protect\cite{Wong2015}.}  
  \label{fig:loopdist}
\end{figure}

@@

Several different approaches for generating three-dimensional
structure models from antibody sequences exist such as
RosettaAntibody\cite{Sircar2009,Sivasubramanian2009}, 
ABodyBuilder\cite{Leem2016}, PIGSPro\cite{Lepore2017} and abYmod,
UCL's in-house software developed by Prof.\ Martin. One of the most
used methods is RosettaAntibody, which implements template selection
and ab initio CDR-H3 loop modelling using loop fragments and employing
specific angle restraints which bias the conformational space towards
so-called `kinked' loops\cite{Schoeder2021,Weitzner2017}. In
contrast, ABodyBuilder uses a database search algorithm
(FREAD\cite{Choi2010}) for CDR loop modelling.

In this project abYmod is used, which is to be found at
\url{http://abymod.abysis.org/}. The program utilizes extensive canonical
class definitions, \VHVL\ angle prediction and a large database of loop
structures (LoopDB) for CDR-H3 modelling to achieve optimal
results. Upon inputting an antibody sequence, abYmod assigns the
canonical class using a set of key residues\cite{Martin1996}and where
an exact match is not possible, a nearest match is made. Then, the
program identifies the 10 best overall-matching PDB files according to
sequence identity for the light and heavy chain. Of these, the best
template is then identified for each CDR using sequence similarity and
identity. In general, modelling the antibody using the single best
overall-matching template works best and the CDR-specific templates
are used if there is no canonical match. The \VHVL\ packing angle is
then determined either using machine learning or the chosen template
structure for one of the chains. CDR specific templates, if selected,
are grafted onto the framework. If there is no template of the correct
length for CDR-H3, the loop is built using the LoopDB database,
containing CDR-H3-like loops from all proteins. Finally, Gromacs energy
minimization software is used to optimize the model. This method has
proven very effective and preliminary analysis suggests the method
achieves comparable results or outperforms other modelling software
(see results section).

Using these mentioned modelling methods, framework regions can
generally be predicted with great accuracy (with better than 1\AA\
RMSD\cite{Almagro2014}), as one can often find a very similar
structure for the homology modelling process.  However, the CDR loops
are not as easily predicted due to their great diversity. If the
canonical conformation of CDR loops 1--5 can be identified, they too
can be modelled rather well, often within 1\AA\ RMSD, for CDR-H3 loops
the average is usually above 3\AA\cite{Almagro2011}.

@@

Modelling the CDR-H3 loop is a hurdle for in silico development of
therapeutic antibodies. Currently, there is no definite, reliable way
to determine how accurate a generated structural model is within the
H3 region. Therefore, the aim of this project will be to produce a
user-friendly predictor of CDR-H3 model quality. The predictor will give
the user an RMSD-range in {\AA}ngstr\"{o}ms, in which the generated model lies
with a high probability. Making such a confidence score available via
the web interface of the in-house modelling software abYmod is a
future goal. Such a score is not provided by most modelling programs
and would thus be a novel addition.  This information can guide the
user in the antibody engineering process. The user has the choice to
determine whether the model is to be used in the intended way, or
whether the model should be re-worked.

\section{Results}
To asses the predictive power regarding the CDR-H3 loop, the software
was tested on a test-set of antibody structures used in the 2014 and
2011 Antibody Modelling Assessments
\cite{Almagro2011,Almagro2014}. As the results depicted in
Figure~\ref{fig:AMA} show, abYmod achieves results similar to, or better than
other modelling programs. However, the outliers with very high RMSD
values increase abYmod's RMSD average. The predictor in this work
would aim to identify such outlier models.

The predictive power of any machine learning model is largely
dependent on the quality and size of the dataset it was trained on. As
this is a non-linear, complex, multi-class classification problem, a
substantial amount of data was required. Thus, an extensive, verified
dataset of antibody structures called abYbank/AbDb\cite{XXXX},
established by Prof.\ Andrew Martin, was utilised (1924 non-redundant
structures). The root-mean-square deviation (RMSD) value, a measure of
distance between backbone \ca\ atoms of superimposed crystal structures
and modelled structures, is calculated (see methods). This metric for
model quality was used to classify models.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{AMA.eps}
  \caption {RMSD values of the CDR-H3 loop for structures from the
    Antibody Modelling Assessment I (2011) and AMAII (2014). abYmod
    outperforms other modelling software in some instances, but also
    has much lower accuracy in few outlier cases. (left: an abYmod
    structure for C705 could be generated, yet the RMSD calculation
    failed. Right: Ab01 is the rabbit antibody PDB:4MA3, which was
    excluded in the CDR-H3 modelling stage in AMAII due to
    difficulties modelling the overall structure previously. Ab01 is
    shown for the methods, where generated models were adequate for
    RMSD calculation.)}
  \label{fig:AMA}
\end{figure}

The full pipeline for creating the final machine learning model that
will predict model quality by giving its RMSD range starts with a
feature-set calculation using the antibody sequence. The feature set
includes many different attributes linked to sequence, physical
characteristics, interactions, etc., within as well as outside of the
loop. There is a plethora of information to train our classifier on,
including packing quality, protrusion, hydrophobicity, pseudo-energy
(see protrusion, hydrophobicity, pseudo-energy (see methods for
details). The sequence logo (Figure~\ref{fig:logo}) visualizes amino acid
occurrence within the loop sequence, elements of which can be
extracted as features \cite{Thomsen2012,Shaner1993}.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{logo.eps}
  \caption {Sequence Logo of the CDR-H3 loop sequence. Data on amino
    acid occurrence taken from \protect\url{http://abymod.abysis.org/} Visualized
    using Seq2Logo.}
  \label{fig:logo}
\end{figure}

After creating the feature dataset, it is pre-processed (cleaning,
scaling, encoding, see methods for details). Structures with a
resolution below 4\AA\ were removed given their low quality. Identical
whole antibody structures were removed from the dataset, while
instances of different antibodies that matched in loop sequence were
not removed. Models of some of these structures with the same loop
sequence differ significantly. The few large RMSD ranges may stem from
low resolution, e.g.\ the highest datapoint contains a structure with a
resolution of 3.00~\AA.  Residue differences near the loop may also
explain the conformational difference. Some of these structures are
complexed while others are not, which may also affect the loop
structure.

The dataset was also screened for any models which abYmod created
using a template sequence from LoopDB, a database of CDR-H3 like loops
from all proteins. This was not the case for any of our structures.

The target data (i.e.\ RMSD values) are then transformed from numerical
values to nominal values so that they can be used for
classification. In order to define these nominal categories, the total
RMSD range must be divided into categories. This is done either by
creating uniform classes i.e.\ 1--2~\AA, 2--3~\AA\ (the optimal size of which
must be determined), etc.\ or by creating balanced classes. When
creating balanced classes, the upper and lower thresholds of a
category are chosen in such a way that each class contains an equal
number of instances. This approach is chosen to counteract the
skewness of the RMSD distribution. However, this was found to
negatively affect the final model's predictive power. Therefore,
uniform classes were used.

They are also transformed into a set of binary values according to a
list of RMSD thresholds. This is done so that binary models can be
trained, which will predict the probability e.g.\ that the model's RMSD
is above 2~\AA, 2.2~\AA, 2.4~\AA, and so on. The number of binary
classifiers incorporated into the first layer have a great effect on
the final model, the general trend being that the more binary
classifiers are used, the better the nominal prediction.

@@

As some features are in the form of amino acid codes, these must be
encoded before they can be passed to a machine learning model. The
encoding strategy often determines how efficiently the model learns
and how much information can be extracted. Different strategies were
employed to represent followed by BLOSUM62 and NLF encoding. The
physiochemical encoding strategy was implemented for all models, being
the most effective. However, PCA-3 BLOSUM62, a dimensionality-reduced
BLOSUM62 encoding method achieved comparable results.

@@

An MCC value of 0.99 was achieved for a classifier predicting whether
an input-model has an RMSD value below 2\AA, 2\AA--4\AA\ or above
4\AA.

>>>>

\newcommand{\e}[1]{\mbox{$\times 10^{#1}$}}
\newcommand{\etal}{~\emph{et al.}}
\newcommand{\degree}{\mbox{${}^{\circ}$}}
\newcommand{\lilian}[1]{{\color{red}{\bfseries Lilian:} #1}}
\newcommand{\andrew}[1]{{\color{green}{\bfseries Andrew:} #1}}
\newcommand{\rewrite}[1]{{\color{blue}{\bfseries Andrew to rewrite:} #1}}
\newcommand{\highlight}[1]{{\color{cyan} #1}}

@@

\begin{abstract}
  Therapeutic antibodies have shown an unprecedented pace of
  development and have brought new hope for the treatment of numerous
  diseases. Bioinformatics tools for modelling antibody structures
  have become invaluable for antibody engineering and the development
  of therapeutic antibodies. The antigen-binding site consists of six
  hypervariable loops, also known as the Complementary Determining
  Regions (CDRs), all of which can be modelled with adequate accuracy,
  except for one. It remains remarkably difficult to model the third CDR
  loop of the antibody heavy chain. CDR-H3 has
  far greater length and sequence variability, with such great structural
  diversity, that modelling it is considerably harder.

  Many approaches for antibody modelling, such as our
  abYmod software, have been developed. Although such efforts have
  improved prediction accuracy the results for CDR-H3 are
  still inconsistent and require further improvement. Providing a
  confidence score for the structure predictions would aid in
  differentiating well-modelled structures from incorrectly modelled
  structures, giving the abYmod user a clearer understanding of the
  generated model reliability.

@@

Antibodies are highly specialized proteins of the immune system that
are produced in response to a foreign substance, called an antigen. A
mature antibody binds a specific antigen with high affinity, while
only weakly interacting with other antigens, or not at all. \lilian{Introduce the use as drugs} This high
affinity and high specificity sets it apart from other pharmaceuticals.
Furthermore, in contrast with small drug molecules, antibodies can not
only bind pockets, but also flat, concave or convex
surfaces\cite{Tavers2001}. Their unique characteristics have enabled 
researchers to develop efficient antibody drugs for treating cancers,
autoimmune disorders, infectious diseases and many more\cite{Lu2020}.
Their ability to target an immense variety of antigens allows for
endless possibilities in application. 
Four of the top 10 best-selling drugs in
2020 were monoclonal antibodies\cite{Urquhart2021}.

In order to design therapeutic antibodies rationally, knowledge of
their structure is essential. The acquired structural information can
be used to increase binding affinity to a target of interest,
predicting both the exact binding site and the antibody stability as
well as assessing immunogenicity\cite{Abhinandan2007}. As
experimental structure determination is costly and time
consuming, computational predictions of an antibody's structure are
used to streamline the process.

The variable
fragment (Fv) of an antibody contains the six complementarity determining regions
(CDRs, also known as hypervariable loops) which form the antigen binding site.
All except one of these loops can be clustered
into a limited number of `canonical structures'\cite{XXXX}. Therefore, modelling
these loops with adequate accuracy is commonly
achievable\cite{North2011,Weitzner2015}. \lilian{Is the second reference relevant here?} However, the CDR loop 3 of the 
heavy chain (CDR-H3) has a far greater sequence variability due to the
processes of V(D)J recombination and somatic hyper‐mutation and its
structure has remained unclassifiable\cite{Finn2016}. The variety in
structure is so great, that its structural diversity is remarkable
even compared to other protein loops\cite{Regep2017}. It was found
that over 75\% of CDR-H3 loops do not have a sub-{\AA}ngstr\"{o}m non-antibody
structural neighbour, while 30\% of CDR-H3 loops have a
completely unique structure compared with under 3\% for all non-antibody
loops\cite{Regep2017}.

Apart from being the most structurally diverse, the CDR-H3 loop is
also the most important for antigen binding, being located at the
center of the binding site and forming the most contacts with the
antigen\cite{MacCallum1996}. It was demonstrated that
differences in this loop alone are sufficient to enable otherwise
identical antibodies to distinguish between various
antigens\cite{Xu2000}.

According to the Kabat definition, the CDR-H3 loop is made up of the
residues 95--105 (using the Kabat\cite{Kabat1992}, Chothia\cite{XXXX} or Martin\cite{XXXX} numbering schemes) in the heavy
chain, with a potential insertion site at position 100. The
possibility of such an insertion of a varying number of residues leads
to a large range of loop lengths, with bovine antibodies being
exceptionally long (Figure~\ref{fig:loopdist}).

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{loopdist.eps}
  \caption{Distribution of CDR-H3 loop lengths in mouse (left),
    human (centre) and cow (right). Mouse and human antibody CDR-H3s
    have a unimodal, yet almost normal distribution with a range of
    $\sim$4--28 and 4--38 respectively. The length cut-off for CDR-H3s
    depicted above is 30 amino acids. Bovine antibodies with
    significantly longer CDR-H3 loops than depicted here exist,
    reaching a length of 67 amino acids and
    above\protect\cite{Wong2015}. \lilian{Do we need this?}}  
  \label{fig:loopdist}
\end{figure}

@@

Several different approaches for generating three-dimensional
structure models from antibody sequences exist such as
RosettaAntibody\cite{Sircar2009,Sivasubramanian2009}, 
ABodyBuilder\cite{Leem2016}, PIGSPro\cite{Lepore2017} \lilian{Lyra, AbLooper} and our own abYmod.
One of the most
used methods is RosettaAntibody, which implements template selection
and \emph{ab initio} CDR-H3 loop modelling using loop fragments and employing
specific angle restraints which bias the conformational space towards
so-called `kinked' loops\cite{Schoeder2021,Weitzner2017}. In
contrast, ABodyBuilder uses a database search algorithm
(FREAD\cite{Choi2010}) for CDR loop modelling.
abYmod \url{http://abymod.abysis.org/} utilizes extensive canonical
class definitions, \VHVL\ angle prediction and a large database of loop
structures (LoopDB) for CDR-H3 modelling.
Upon inputting an antibody sequence, abYmod assigns the
canonical class using a set of key residues\cite{Martin1996} and where
an exact match is not possible, a nearest match is made. \rewrite{Then, the
program identifies the 10 best overall-matching PDB files according to
sequence identity for the light and heavy chain. Of these, the best
template is then identified for each CDR using sequence similarity and
identity. In general, modelling the antibody using the single best
overall-matching template works best and the CDR-specific templates
are used if there is no canonical match.}

The \VHVL\ packing angle is
then determined either using machine learning \lilian{not yet!} or the chosen template
structure for one of the chains. CDR specific templates, if selected,
are grafted onto the framework. If there is no template of the correct
length for CDR-H3, the loop is built using LoopDB,
containing CDR-H3-like loops from all proteins. Finally, Gromacs energy
minimization software is used to optimize the model. This method has
proven very effective and preliminary analysis suggests the method
achieves comparable results or outperforms other modelling software
(see results section).

Using these mentioned modelling methods, framework regions can
generally be predicted with great accuracy (with better than 1~\AA\
RMSD\cite{Almagro2014}), as one can often find a very similar
structure for the homology modelling process.  However, the CDR loops
are not as easily predicted due to their great diversity. If the
canonical conformation of CDR loops CDR-L1--L3 and CDR-H1--H2 can be identified, they too
can be modelled rather well, often within 1~\AA\ RMSD, for CDR-H3 loops
the \lilian{not sure what average and usually mean} average is usually above 3~\AA\cite{Almagro2011}.

@@

Modelling the CDR-H3 loop is a hurdle for \emph{in silico} development of
therapeutic antibodies. Currently, there is no definite, reliable way
to determine how accurate a generated structural model is within the
H3 region. Therefore, we have produced a
user-friendly predictor of CDR-H3 model quality. The predictor will give
the user an RMSD-range in {\AA}ngstr\"{o}ms, in which the generated model lies
with a high probability.
This information can guide the
user in the antibody engineering process. The user has the choice to
determine whether the model is to be used as is, or
whether the model should be re-worked.

\section{Results}
The software
was tested on a test-set of antibody structures used in the 2014 and
2011 Antibody Modelling Assessments
\cite{Almagro2011,Almagro2014}. As the results depicted in
Figure~\ref{fig:AMA} show, abYmod achieves results similar to, or better than,
other modelling programs. However, the outliers with very high RMSD
values increase abYmod's RMSD average. The predictor in this work
would aim to identify such outlier models.

The predictive power of any machine learning model is largely
dependent on the quality and size of the dataset on which it was trained. As
this is a non-linear, complex, multi-class classification problem, a
substantial amount of data was required. Thus, an extensive, verified
dataset of antibody structures called abYbank/AbDb\cite{XXXX},
was utilised (1924 non-redundant
structures). The \ca\ root-mean-square deviation (RMSD) value
between the crystal structures
and modelled structures was calculated (see Methods) and
was used to classify models.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{AMA.eps}
  \caption {RMSD values of the CDR-H3 loop for structures from the
    Antibody Modelling Assessment I (2011) and AMAII (2014). abYmod
    outperforms other modelling software in some instances, but also
    has much lower accuracy in few outlier cases. Left: an abYmod
    structure for C705 could be generated, yet the RMSD calculation
    failed \lilian{Why? I'm sure we can resolve this!}.
    Right: Ab01 is the rabbit antibody PDB:4MA3, which was
    excluded in the CDR-H3 modelling stage in AMAII due to
    difficulties modelling the overall structure previously. Ab01 is
    shown for the methods, where generated models were adequate for
    RMSD calculation. \lilian{This needs better explanation}}
  \label{fig:AMA}
\end{figure}

The full pipeline for creating the final machine learning model
starts with 
feature-set calculation using the antibody sequence. The feature set
includes attributes linked to sequence, structure, physical
characteristics, interactions, etc., within, as well as outside, the
loop. 
The sequence logo (Figure~\ref{fig:logo}) visualizes amino acid
occurrence within the loop sequence, elements of which can be
extracted as features \cite{Thomsen2012,Shaner1993}.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{logo.eps}
  \caption {Sequence Logo of the CDR-H3 loop sequence. Data on amino
    acid occurrence taken from \protect\url{http://abymod.abysis.org/} Visualized
    using Seq2Logo. \lilian{What's the X-axis numbering? IMGT? Can you highlight the CDR residues (95--122) What range of lengths is included?}}
  \label{fig:logo}
\end{figure}

After creating the feature dataset, it is pre-processed (cleaning,
scaling, encoding, see methods for details). Structures with a
resolution worse than 4~\AA\ were removed.
\lilian{You already said it was a non-redundant set?} \highlight{Identical
whole antibody structures were removed from the dataset}, \lilian{I don't understand this bit!} \highlight{while
instances of different antibodies that matched in loop sequence were
not removed}. Models of some of these structures with the same loop
sequence differ significantly. The few large RMSD ranges may stem from
low resolution. For example, the \highlight{highest} \lilian{What does `highest' mean?} datapoint contains a structure with a
resolution of 3.00~\AA.  \lilian{Explain} \highlight{Residue differences near the loop may also
explain the conformational difference}. Some of these structures are
complexed while others are not, which may also affect the loop
structure (manuscript in preparation).

The target data (i.e.\ RMSD values) are transformed from numerical
values to nominal values so that they can be used for
classification. In order to define these nominal categories, the total
RMSD range must be divided into categories. This is done either by
creating uniform classes i.e.\ 1--2~\AA, 2--3~\AA, etc., (the optimal size of which
must be determined), or by creating balanced classes. When
creating balanced classes, the upper and lower thresholds of a
category are chosen in such a way that each class contains an equal
number of instances. This approach was chosen to counteract the
skewness of the RMSD distribution. However, this was found to
affect the final model's predictive power negatively. Therefore,
uniform classes were used.

They are also transformed \lilian{explain?} into a set of binary values according to a
list of RMSD thresholds. This is done so that binary models can be
trained, which will predict the probability e.g.\ that the model's RMSD
is above 2~\AA, 2.2~\AA, 2.4~\AA, and so on. The number of binary
classifiers incorporated into the first layer has a great effect on
the final model, the general trend being that the more binary
classifiers are used, the better the nominal prediction. \lilian{Data?}

@@

As some features are in the form of amino acid names, these must be
encoded before they can be passed to a machine learning model. The
encoding strategy often determines how efficiently the model learns
and how much information can be extracted. Different strategies were
employed to represent followed by BLOSUM62 and NLF encoding. The
physiochemical encoding strategy was implemented for all models, being
the most effective. However, PCA-3 BLOSUM62, a dimensionality-reduced
BLOSUM62 encoding method achieved comparable results.

@@

An MCC value of 0.99 was achieved for a classifier predicting whether
an input-model has an RMSD value below 2~\AA, 2~\AA--4~\AA\ or above
4~\AA.
